Improving the Image Acquisition Rate of an Atomic Force Microscope Through Compressive Sampling

### 2019-06-15 latex/afm-cs-main.tex
Update data automagically with catchfilebetween tags. Re-work some of the results section.

\usepackage{showframe}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{graphicx}		% to insert figures
\usepackage{multirow}
\usepackage{cite}
\usepackage{listings}
\usepackage{booktabs}
\usepackage[percent]{overpic}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage[inkscapelatex=false, inkscapepath=svgsubpath]{svg}
\usepackage{url}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{placeins}
\usepackage{todonotes}

@@

% *******************************************************************************
% This artificially increases the papersize and margins, so todo notes are legible.
% ***************** WARNING: comment this out for final version. ****************
\usepackage[paperwidth=734.295pt, textwidth=516pt,
            marginparsep=5pt, hoffset=10pt, marginparwidth=90pt,
            textheight=696pt]{geometry}
% Use layouts to display the original dimensions, so we can get as close to that as possible with
% our fake page size.
\usepackage{layouts}
%textwidth: \printinunitsof{in}\prntlen{\textwidth}
%linewidth: \printinunitsof{in}\prntlen{\linewidth}
% textwidth: \printinunitsof{in}\prntlen{\textheight}

@@

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim to reduce
  the time to acquire an image by reducing the number of measurements needed
  while still maintaining image quality. In this paper, we describe a hardware
  implementation and demonstration of one such approach based on the use of
  collections of short scans known as $\mu$--paths. Using a commercial AFM, we
  acquire data on a grating sample.
  %using two different sampling
  %approaches: randomly-placed $\mu-$paths and $\mu-$paths designed to minimize
  %the reconstruction error based on partial prior information about the spatial
  %frequency content in the sample image.
  Reconstructions are made from these data using
  %three approaches: (1) inpainting, an interpolation technique that
  %diffuses information from sampled locations into unsampled regions, (2)
  %basis-pursuit, a compressive sensing-based algorithm that seeks to minimize a
  %measure of sparsity in the underlying image, and (3)
  a new variant of basis
  pursuit, Basis Pursuit with Vertical Variation (BPVV), that is designed to reduce
  artifacts arising from the sampling pattern. The quality of the resulting
  images is compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio and the
  structured similarity index metric
  and a new metric we call the relative damage index.
  \todo{Re-write abstract, especially conclusions}
  These experiments demonstrate that at slow
  scan rates, the $\mu-$path scheme produces similar image quality with
  significantly less sampling (and thus less tip-sample interaction) and that at
  high rates, the undersampling scheme produces higher quality images than
  raster scanning.
\end{abstract}

@@

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\columnwidth]{figures-SBA/random_mask.pdf}
  \caption{An example of the horizontal $\mu$-path sampling pattern for a 256$\times$256 pixel image with 35 pixels in each short scan and a total of 20\% pixels scanned.}
  \label{fig:mu_mask}
\end{figure}
% =========================================================================
\subsection{Reconstruction methods}
\label{sec:reconstructionMethods}
Compressive sensing (CS) is a signal processing technique which aims at signal reconstruction from a
relatively small (sub-Nyquist limit) number of measurements
\cite{carmi2014compressive}. It takes advantage of the approximate sparsity of
real-world signals, that is, that many coefficients of such signals
are close to zero when represented in an appropriate basis. CS methods seek the
true image signal $x\in\mathbb{R}^n$ from the observation equation,
\begin{equation}\label{op:observation}
  y = R x = RU\eta,
\end{equation}
\noindent where $y\in\mathbb{R}^n$ is the observation vector, $R$ is an
$n\times m$ matrix defining the measurements, $U$ is an $m\times m$ sparsity
basis and $\eta$ is the sparse representation of $x$ in the domain of $U$. In
general, $n\ll m$. In an imaging application, where the underlying signal is a
matrix $X\in\mathbb{R}^{h\times s}$, we take $x=\text{vec}(X)$, where the
$\text{vec}(\cdot)$ operator stacks the columns of a matrix.

In the AFM application, the probe can only measure a single pixel at a time.
Thus the rows of $R$ are a subset of the rows of an $m$ by $m$ identity matrix.
Ideally, the sparsity basis and
the measurement matrix $R$ will have a low \textit{mutual coherence}, a
measure that describes how each of the rows of $R$ (the measurements)
``spreads out'' in the domain of $U$ \cite{candes2007sparsity}.
In the following, we assume that $U^TU=I$, though in the simulation and
experimental results, we take $U$ as the Discrete Cosine Transform (DCT) basis.
The DCT basis generally keeps a good balance between achieving a low
mutual coherence between $U$ and the $\mu$-path sensing
matrices $R$ and providing a high sparsity for typical AFM sample images.

@@

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed} as these
longer paths lead to increased mutual coherence between the measurement matrix
$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
tip re-engagements and thus shorter scan times.
\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[ht!]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV}
    & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    \includesvg[width=0.16\textwidth]{figures/cs20ng_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv_zoom.svg}\\
    % 
    % ------------------------------ Row  2 --------------------------------------------
    \includesvg[width=0.16\textwidth]{figures/dna_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv_zoom.svg}
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\todo{Re-do this figure???}
\endgroup

\todo{This development is way too long!}
To mitigate these affects, we propose a new variant of BPDN that we term basis pursuit with
vertical variation (BPVV). BPVV adds a vertical total variation penalty in the spatial domain to the
optimization objective. That is, \eqref{op:bp} is modified to
\todo{It has been my observation that some benefit is gained by including $D_h$, but weighting it less than $D_v$. Not sure if we should leave it in. If so, BPVV should be BPTV or something.}
\begin{align}
  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} \left\|U^Tx\right\|_1
                         + \alpha\left\|D_vx\right\|_1
                         + \beta\left\|D_hx\right\|_1 \label{op:bp_tv}\\
                       &=\min_{x\in Q_p} \left\|W^Tx\right\|_1 \label{op:bp_tvW}
                         % \quad W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T \nonumber
\end{align}
where
\begin{equation*}
W = \begin{bmatrix}U^T&\alpha D_h&\beta D_v \end{bmatrix}
\end{equation*}
with ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) representing a 
discrete gradient of a matrix in the vertical (resp., horizontal) direction (see, e.g., \cite[Section 6.1,]{becker_nesta_2011}). 
% and
% \begin{align*}
%   (\nabla_v X)_{i,j} = 
%   \begin{cases}
%     X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
%     0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
%   \end{cases}\\
%   (\nabla_h X)_{i,j} = 
%   \begin{cases}
%     X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
%     0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
%   \end{cases}
% \end{align*}
Thus, in \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
The parameters $\alpha$ and $\beta$ are weighting parameters.
The description of BPVV in \eqref{op:bp_tvW} can be interpreted as changing our assumption of sparsity in the DCT basis to assuming sparsity in an overcomplete dictionary \cite{candes_redundant_2011}.
\todo{I believe this is correct: Sean/Yufan can you confirm or reject?}

Moreover, when written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}.

@@

A comparison between BPDN and BPVV is shown in
Fig.~\ref{fig:BPTV_demonstration}. The first column two raster scans: the top is 512 by 512 pixel image of a CS20NG grating acquired with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of DNA acquired with an Agilent 5500 AFM.
For the CS20NG grating, we sampled 15\% of the pixels with 50 pixel $\mu$-paths. We sampled 25\% of the DNA image with 25 pixel long $\mu$-paths. The second columns shows the full frame reconstructions using BPDN and the third columns shows the result using BPVV. The fourth column zooms in on the region indicated by the red box in column one. Similarly, the fifth and six columns show the detail of the reconstructions. The reconstruction results show the artifacts apparent in the BPDN reconstruction are largely
mitigated using BPVV. Thus, in the remainder of the paper, we focus exclusively on BPVV. As for reconstruction time, it took about 1.5 seconds to reconstruct the DNA image and about 7 seconds for the CS20NG.

@@

Through a breakout box, the Agilent 5400 provides access to the $z$-axis deflection signal. When the Agilent software is set to open-loop mode, a $\pm10$~volt input on the standard control box allows control of the $z$-axis of the N9524a piezo scanner, which has a total range of 7 $\mu$m.
Initial (course) engagement of the tip to the
sample is performed using the PicoView software before control is handed over to
the custom controllers.

@@

Implementing the $\mu$-path scheme involves operating the AFM in several
distinct stages. In the $xy$-direction, the system must transition from tracking
a step command (in the transition to a new measurement location) to tracking a
scan pattern. For our simple integral controller, this only involves changing
the reference signals $x_{ref}$ and $y_{ref}$.
In the $z$-direction, the system
must transition between tip descent, surface scanning, tip retraction, and
maintaining a $z$-axis position.

@@

\subsection{Control}\label{sec:control}
\begin{figure}
  \centering
  \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
  \caption{FRFs of the $Z$-axis. The blue curve is the open loop response from $u_Z$ to deflection. By inverting the bending mode at 215~Hz, we achieve the black curve in closed-loop.}
  \label{fig:z_control}
\end{figure}

The control structure for each axis is similar and essentially consists of a set of filters in series with a PI controller. The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} (black curve) and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes (red curves). The first resonance of each axis is the bending mode. For the $Z$ axis, this resonance is at 215~Hz and at approximately 350~Hz for the $X$ and $Y$ axes.

The filter for the $Z$-axis controller inverts the complex-conjugate pole-zero pair at 215~Hz. This allows the gain of the PI controller to be increased substantially. The closed-loop achieves a bandwidth of about 450~Hz, as shown by the black curve in Fig.~\ref{fig:z_control}.

We take a similar approach to the $X$ and $Y$ axes. The filter inverts the bending modes at 350~Hz and adds a notch filter for the main resonant peak at 650~Hz. The resulting closed-loops are shown in the (1,1) and (2,2) positions of Fig.~\ref{fig:mimo_frf_uxuy}. In general, the $X$-axis positioning requirements are more stringent for both CS and raster scanning

Unfortunately, as Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong cross-coupling between the axes. The coupling from the horizontal plane to the $Z$ axis is particularly problematic and our SISO control scheme does little to attenuate the resonances of $G_{Z,u_X}$ and $G_{Z,u_Y}$. In particular, there are modes in both these transfer functions at 215 and 505 Hz that do not appear in a SISO model of $G_{X,u_x}$ or $G_{y,u_Y}$.

For raster scans, the frequency content of the $X$-axis reference (which is a triangle wave) decays like $1/n^2$ with a gain proportional to the raster frequency. In contrast, the $X$-axis reference for a $\mu$-path scan is composed of a sequence of steps and ramps. The inclusion of the (discontinuous) steps means we should expect the $\mu$-path $X$ reference to decay like $1/n$. 
Thus,  while the cross-coupling can induce $Z$-axis vibrations for faster raster scans, it is especially problematic for $\mu$-path scanning. In principle, one could mitigate these issues with a full MIMO control design. In this work, we opt for a much simpler feedforward scheme described in the next subsection.

% The control law used for the $Y$-axis is a simple PI controller of the
% form
% \begin{equation}
%   \frac{U(z)}{E_Y(z)}=D(z) = \frac{K_Iz}{z-1},
%   \label{eqn:dzI}
% \end{equation}
% where, the error signal $E_Y(z) = Y(z)-R_Y$.
% 
% \todo{Should I implement something better for $Y$-axis, e.g., cancel complex
%   pole-zeros at 350 hz and add notch filter???}

% The $Z$-axis control is slightly more complicated than the simple $Y$-axis
% integral controller and is described in the following subsection.
% \subsection{Z-axis Control Design}\label{sec:zaxis_cs_control}
% The main challenge to increasing the $Z$-axis bandwidth is the bending mode
% resonance at 215 Hz, which can be seen in the FRF from $u_Z$ to $Z_{d}$ in
% Fig.~\ref{fig:z_control} (blue curve). We address this by inverting the complex
% pole-zero pair at 215 Hz. Thus, the entire $Z$-axis controller consists of a PI
% controller, $D_I(z)$ cascaded with the resonance inversion, $D^{-1}(z)$, as shown in Fig.~\ref{fig:afm_bd_dinv}. The DC-gain
% of $D$ is (approximately) the same as the DC-gain of the plant.
% The inclusion of $D^{-1}$ allows us to substantially increase the PI gain and
% achieve a closed-loop bandwidth of about 480 Hz. This is the black curve in Fig.~\ref{fig:z_control}.

@@

\subsection{Feedforward Control}\label{sec:ff_control}
% In our AFM, there is a strong coupling between the horizontal axes and vertical deflection. Fig.~\ref{fig:mimo_frf_uxuy} shows a MIMO FRF for $u_X$ and $u_Y$ to the outputs in each axis. The dotted black curves are the open loop responses and the dashed red curves are the nominal closed-loop responses. Though the $Z$-direction inputs are not shown, the closed loop responses include the $Z$-axis controller. Note that, especially for $H_{z,u_X}$, the closed-loop response is barely improved over the open loop response and in particular, there is a sharp resonance at 215~Hz and 505~Hz. To deal with this, we employ two different strategies for CS and raster scanning.

For CS scanning, we insert a feed-forward filter with three notches, one at 215~Hz, one at 350~Hz and one at 505~Hz. We design a similar feed-forward filter for the $Y$-axis. Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the solid pink curves and the resulting overall FRF is shown as the solid blue curves, which show a dramatic reduction in the cross coupling. A similar affect could be achieve by using a simple low-pass filter. However, to achieve the same 40~dB of attenuation of the mode at 215 Hz, would require, e.g., that a two-pole LPF have its cut-off frequency at about 20~Hz.

For raster scanning, we use a truncated Fourier series, where each Fourier coefficient is scaled by the inverse of the closed-loop FRF at the corresponding frequency. We truncate this series such that the highest frequency is smaller than 200 Hz. See, e.g., \cite{clayton_review_2009} for more details on this strategy. Note that this scheme implies that the effective bandwidth of the $X$-axis controller is higher while raster scanning than while CS-scanning. On the other hand, it also implies that the for faster scan rates, fewer Fourier coefficients are used, and so the approximation to a triangle wave is worse.
\begin{figure}
  \includesvg[width=1\columnwidth]{figures/with_wo_ff.svg}
  \caption{Scans over mica. (left) Without feedforward. (right) with feedforward.}
  \label{fig:with_ff}
\end{figure}

>>>>

\usepackage{showframe}
\usepackage{amssymb}		% to get all AMS symbols
\usepackage{amsthm}
\usepackage{mathtools}
\usepackage{graphicx}		% to insert figures
\usepackage{multirow}
\usepackage{cite}
\usepackage{listings}
\usepackage{booktabs}
\usepackage[percent]{overpic}
\usepackage{subcaption}
\usepackage{xspace}
\usepackage{enumitem}
\usepackage[inkscapelatex=false, inkscapepath=svgsubpath]{svg}
\usepackage{url}
\usepackage[ruled,linesnumbered]{algorithm2e}
\usepackage{placeins}
\usepackage[disable]{todonotes}

@@

\usepackage{catchfilebetweentags} % for data input
\newcommand{\scanD}[1]{\ExecuteMetaData[cs_data.txt]{#1}}
\newcommand{\baseline}[1]{\ExecuteMetaData[baseline_errors.txt]{#1}}

% *******************************************************************************
% This artificially increases the papersize and margins, so todo notes are legible.
% ***************** WARNING: comment this out for final version. ****************
%\usepackage[paperwidth=734.295pt, textwidth=516pt,
%            marginparsep=5pt, hoffset=10pt, marginparwidth=90pt,
%           textheight=696pt]{geometry}
% Use layouts to display the original dimensions, so we can get as close to that as possible with
% our fake page size.
%\usepackage{layouts}
%textwidth: \printinunitsof{in}\prntlen{\textwidth}
%linewidth: \printinunitsof{in}\prntlen{\linewidth}
% textwidth: \printinunitsof{in}\prntlen{\textheight}

@@

\maketitle
\begin{abstract}
  Undersampling-based approaches in Atomic Force Microscopy (AFM) aim to reduce
  the time to acquire an image by reducing the number of measurements needed
  while still maintaining image quality. In this paper, we describe a hardware
  implementation and demonstration of one such approach based on the use of
  collections of short scans known as $\mu$--paths. Using a commercial AFM, we
  acquire data on a grating sample.
  Reconstructions are made from these data using
  %three approaches: (1) inpainting, an interpolation technique that
  %diffuses information from sampled locations into unsampled regions, (2)
  %basis-pursuit, a compressive sensing-based algorithm that seeks to minimize a
  %measure of sparsity in the underlying image, and (3)
  a new variant of basis
  pursuit, Basis Pursuit with Vertical Variation (BPVV), that is designed to reduce
  artifacts arising from the sampling pattern. The quality of the resulting
  images is compared to images from standard raster scans of the same regions at
  comparable imaging rates using both the peak signal-to-noise ratio and the
  structured similarity index metric
  and a new metric we call the relative damage index.
  \todo{Re-write abstract, especially conclusions}
  These experiments demonstrate that at slow
  scan rates, the $\mu-$path scheme produces similar image quality with
  significantly less sampling (and thus less tip-sample interaction) and that at
  high rates, the undersampling scheme produces higher quality images than
  raster scanning.
\end{abstract}

@@

\textbf{Contributions}
Much of the prior work on undersampled AFM images is based purely on simulations \cite{han_optimal_2018, Luo_nano_2015, oxvig_structure_2017, jensen_reconstruction_2013, maxwell_acc_2014, Chen_2012jx}.

@@

\begin{figure}
  \centering
  \includegraphics[width=0.7\columnwidth]{figures-SBA/random_mask.pdf}
  \caption{An example of the horizontal $\mu$-path sampling pattern for a 256$\times$256 pixel image with 35 pixels in each short scan and a total of 20\% pixels scanned.}
  \label{fig:mu_mask}
\end{figure}
% =========================================================================
\subsection{Reconstruction methods}
\label{sec:reconstructionMethods}
Compressive sensing (CS) is a signal processing technique which aims at signal reconstruction from a
relatively small (sub-Nyquist limit) number of measurements
\cite{carmi2014compressive}. It takes advantage of the approximate sparsity of
real-world signals, that is, that many coefficients of such signals
are close to zero when represented in an appropriate basis. CS methods seek the
true image signal $x\in\mathbb{R}^n$ from the observation equation,
\begin{equation}\label{op:observation}
  y = R x = RU\eta,
\end{equation}
\noindent where $y\in\mathbb{R}^m$ is the observation vector, $R$ is an
$n\times m$ matrix defining the measurements, $U$ is an $m\times m$ sparsity
basis and $\eta$ is the sparse representation of $x$ in the domain of $U$. In
general, $n\ll m$. In an imaging application, where the underlying signal is a
matrix $X\in\mathbb{R}^{h\times s}$, we take $x=\text{vec}(X)$, where the
$\text{vec}(\cdot)$ operator stacks the columns of a matrix.

In the AFM application, the probe can only measure a single pixel at a time.
Thus the rows of $R$ are a subset of the rows of an $m$ by $m$ identity matrix.
Ideally, the sparsity basis and
the measurement matrix $R$ will have a low \textit{mutual coherence}, a
measure that describes how each of the rows of $R$ (the measurements)
``spreads out'' in the domain of $U$ \cite{candes2007sparsity}.
In the following, we assume that $U^TU=I$, though in the simulation and
experimental results, we take $U^T$ as the Discrete Cosine Transform (DCT).
The DCT basis generally keeps a good balance between achieving a low
mutual coherence between $U$ and the $\mu$-path sensing
matrices $R$ and providing a high sparsity for typical AFM sample images.

@@

Although BPDN is effective in the general setting, using it for reconstruction
from horizontal $\mu$-path samples often yields artifacts in the vertical
direction (that is, the direction orthogonal to the $\mu$-path scans) leading to
strong discontinuities in the image. These artifacts grow more prominent as the
length of the $\mu$-paths is increased \cite{maxwell2014compressed}, because these
longer paths lead to increased mutual coherence between the measurement matrix
$R$ and the sparsity basis $U$. However, longer $\mu$-paths means fewer
$\mu$-paths and thus shorter scan times.
\noindent 
\begingroup \setlength{\tabcolsep}{1pt}
\begin{figure*}[ht!]
  \centering
  \begin{tabular}{cccccc}
    \textit{\small original image} & \textit{\small BPDN} & \textit{\small BPVV}
    & \textit{\small detail of original} & \textit{\small detail of BPDN} & \textit{\small detail of BPVV} \\
    \includesvg[width=0.16\textwidth]{figures/cs20ng_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bp_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/cs20ng_bptv_zoom.svg}\\
    % 
    % ------------------------------ Row  2 --------------------------------------------
    \includesvg[width=0.16\textwidth]{figures/dna_og.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_og_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bp_zoom.svg}
    %
    & \includesvg[width=0.16\textwidth]{figures/dna_bptv_zoom.svg}
  \end{tabular}
  \caption{Reconstruction comparison between BPDN and BPVV. (first column)
    Original raster-scanned image. (second column) BPDN reconstruction from
    random, 40 pixel long $\mu$-paths with 25\% sampling. (third column) BPVV
    reconstruction from the same sub-sampled data. (remaining columns)
    Corresponding details from the red boxes indicated in the raster image. The
    results show that BPVV reduces the artifacts arising from the horizontal
    scans of the $\mu$-path pattern that appear in BPDN reconstructions.}
  \label{fig:BPTV_demonstration}
\end{figure*}
\endgroup

To mitigate these affects, we propose a new variant of BPDN that we term basis pursuit with
vertical variation (BPVV). BPVV adds a vertical total variation penalty in the spatial domain to the
optimization objective. That is, \eqref{op:bp} is modified to
\todo{It has been my observation that some benefit is gained by including $D_h$, but weighting it less than $D_v$. Not sure if we should leave it in. If so, BPVV should be BPTV or something.}
\begin{align}
  \min_{x\in Q_p}~f(x) &= \min_{x\in Q_p} \left\|U^Tx\right\|_1
                         + \alpha\left\|D_vx\right\|_1
                         + \beta\left\|D_hx\right\|_1 \label{op:bp_tv}\\
                       &=\min_{x\in Q_p} \left\|W^Tx\right\|_1 \label{op:bp_tvW}
                         % \quad W = \begin{bmatrix}U&\alpha_hD^T_h&\alpha_vD^T_v \end{bmatrix}^T \nonumber
\end{align}
where
\begin{equation*}
W = \begin{bmatrix}U^T&\alpha D_h&\beta D_v \end{bmatrix}
\end{equation*}
with ${D_v x=\text{vec}(\nabla_v X)}$ (resp., ${D_v x=\text{vec}(\nabla_v X)}$) representing a 
discrete gradient of a matrix in the vertical (resp., horizontal) direction (see, e.g., \cite[Section 6.1,]{becker_nesta_2011}). 
% and
% \begin{align*}
%   (\nabla_v X)_{i,j} = 
%   \begin{cases}
%     X_{i+1,j} - X_{i,j}, & 1\leq i<h,~ 1\leq j\leq s,\\
%     0, & \phantom{:}i=h,~\phantom{:::::} 1\leq j\leq s.
%   \end{cases}\\
%   (\nabla_h X)_{i,j} = 
%   \begin{cases}
%     X_{i,j+1} - X_{i,j}, & 1\leq i\leq h,~1\leq j<s \\
%     0, & \phantom{}1\leq i\leq,~\phantom{:::} j=s
%   \end{cases}
% \end{align*}
Thus, in \eqref{op:bp_tv}, $\left \| D_v x \right \|_1$ (resp., $\left \| D_h x \right \|_1$) is the total variation (TV) of the signal in the vertical (resp., horizontal) direction.
The parameters $\alpha$ and $\beta$ are weighting parameters.
The description of BPVV in \eqref{op:bp_tvW} can be interpreted as changing our assumption of sparsity in the DCT basis to assuming sparsity in an overcomplete dictionary \cite{candes_redundant_2011}.
\todo{I believe this is correct: Sean/Yufan can you confirm or reject?}
When written as \eqref{op:bp_tvW}, the problem is in a form that may be solved with NESTA~\cite{becker_nesta_2011}.

@@

A simulation comparison between BPDN and BPVV is shown in
Fig.~\ref{fig:BPTV_demonstration}. The first column shows two raster scans: the top is 512 by 512 pixel image of a CS20NG grating acquired with an Agilent 5400 AFM and the bottom is a 256 by 256 pixel image of DNA acquired with an Agilent 5500 AFM.
For the CS20NG grating, we sampled 15\% of the pixels with 50 pixel $\mu$-paths. We sampled 25\% of the DNA image with 25 pixel long $\mu$-paths. The second columns shows the full frame reconstructions using BPDN and the third columns shows the result using BPVV. The fourth column zooms in on the region indicated by the red box in column one. Similarly, the fifth and six columns show the detail of the reconstructions. The reconstruction results show the artifacts apparent in the BPDN reconstruction are largely
mitigated using BPVV. Thus, in the remainder of the paper, we focus exclusively on BPVV. As for reconstruction time, it took about 1.5 seconds to reconstruct the DNA image and about 7 seconds for the CS20NG.

@@

Through a breakout box, the Agilent 5400 provides access to the $Z$-axis deflection signal. When the Agilent software is set to open-loop mode, a $\pm10$~volt input on the standard control box allows control of the $Z$-axis of the N9524a piezo scanner, which has a total range of 7 $\mu$m.
Initial (course) engagement of the tip to the
sample is performed using the PicoView software before control is handed over to
the custom controllers.

@@

Implementing the $\mu$-path scheme involves operating the AFM in several
distinct stages. In the $XY$-direction, the system must transition from tracking
a step command (in the transition to a new measurement location) to tracking a
scan pattern. For our simple integral controller, this only involves changing
the reference signals $X_{ref}$ and $Y_{ref}$.
In the $Z$-direction, the system
must transition between tip descent, surface scanning, tip retraction, and
maintaining a $Z$-axis position.

@@

\subsection{Control}\label{sec:control}
\begin{figure}
  \centering
  \includesvg[width=1\columnwidth]{figures/z_control_design.svg}
  \caption{FRFs of the $Z$-axis. The blue curve is the open loop response from $u_Z$ to deflection. By inverting the bending mode at 215~Hz, we achieve the black curve in closed-loop.}
  \label{fig:z_control}
\end{figure}
The control structure for each axis, shown in the block diagram in Fig.~\ref{fig:afm_bd_dinv}, is similar and essentially consists of a set of filters in series with a PI controller. The open-loop frequency response for the $Z$-axis is shown in Fig.~\ref{fig:z_control} and in Fig.~\ref{fig:mimo_frf_uxuy} for the $X$ and $Y$ axes as the black curves. The first resonance of each axis is the bending mode, which appears at 215~Hz for the $Z$ axis and about 350~Hz for the $X$ and $Y$ axes.

The filter portion of the $Z$-axis controller $D_Z$ is second-order and simply inverts the complex-conjugate pole-zero pair at 215~Hz. This allows the gain of the PI controller to be increased substantially. The closed-loop achieves a bandwidth of about 450~Hz, as shown by the black curve in Fig.~\ref{fig:z_control}. Without this inversion, the bandwidth is limited to about 50~Hz.

We take a similar approach for the $X$ and $Y$ axes. The filters $D_x$ and $D_y$ invert the bending modes at 350~Hz and add notch filters at the main resonant peaks near 650~Hz. The resulting closed-loop transfer functions are shown as the red curves in Fig.~\ref{fig:mimo_frf_uxuy}.

In general, the $X$-axis positioning requirements are more stringent for both CS and raster scanning. BLA BLAH hysteresis and creep. Thus, the $X$-axis compensator also includes an inverse creep and hysteresis model. The hysteresis model is a modified Prandtl-Ishlinki type model and is based on the work of \cite{kuhnen_modeling_2003}, while the drift compensation models the piezo creep as a simple second order transfer function with real poles and zeros. In Fig.~\ref{fig:afm_bd_dinv}, the hysteresis inversion is indicated by $\mathcal{H}^{-1}[\cdot]$. We have found that the inclusion of these extra compensators limits the overshoot of the $X$-axis during larger moves between different $\mu$-paths. More details on fitting the creep and hysteresis models can be found in our other work \cite{braker_afmmpc_2019}.

@@

\subsection{Feedforward Control}\label{sec:ff_control}
% In our AFM, there is a strong coupling between the horizontal axes and vertical deflection. Fig.~\ref{fig:mimo_frf_uxuy} shows a MIMO FRF for $u_X$ and $u_Y$ to the outputs in each axis. The dotted black curves are the open loop responses and the dashed red curves are the nominal closed-loop responses. Though the $Z$-direction inputs are not shown, the closed loop responses include the $Z$-axis controller. Note that, especially for $H_{z,u_X}$, the closed-loop response is barely improved over the open loop response and in particular, there is a sharp resonance at 215~Hz and 505~Hz. To deal with this, we employ two different strategies for CS and raster scanning.
Unfortunately, as the bottom panel of Fig.~\ref{fig:mimo_frf_uxuy} makes clear, there is a strong cross-coupling from the horizontal plane to the $Z$ axis (the coupling from $u_Z$ to the $X$ and $Y$ axes is very weak, and so is not shown). Our SISO control scheme does little to attenuate the resonances of $G_{Z,u_X}$ and $G_{Z,u_Y}$. In particular, there are modes in both these transfer functions at 215 and 505 Hz that do not appear in a SISO model of $G_{X,u_X}$ or $G_{Y,u_Y}$.

For raster scans, the frequency content of the $X$-axis reference (which is a triangle wave) decays like $1/n^2$ with a gain proportional to the raster frequency. In contrast, the $X$-axis reference for a $\mu$-path scan is composed of a sequence of steps and ramps. The inclusion of the (discontinuous) steps means we should expect the $\mu$-path $X$ reference to decay like $1/n$. 
Thus,  while the cross-coupling can induce $Z$-axis vibrations for faster raster scans, it is especially problematic for $\mu$-path scanning. This is illustrated in the left column of Fig.~\ref{fig:with_ff}, which shows a CS cycle during which the $X$-axis makes a 5 micron move, which induces excessively large vibrations in the vertical control.

In principle, one could mitigate these issues with a full MIMO control design. In this work, we opt for a much simpler feedforward scheme.
For CS scanning, we insert feed-forward filters ($F_X$ and $F_Y$ in Fig.~\ref{fig:afm_bd_dinv}) with three notches: one at 215~Hz, one at 350~Hz and one at 505~Hz. We design a similar feed-forward filter for the $Y$-axis. Both filters are shown in Fig.~\ref{fig:mimo_frf_uxuy} as the solid pink curves and the resulting overall FRF is shown as the solid blue curves, which show a dramatic reduction in the cross coupling. A similar affect could be achieve by using a simple low-pass filter. However, to achieve the same 40~dB of attenuation of the mode at 215 Hz, would require, e.g., that a two-pole low-pass filter have its cut-off frequency at about 20~Hz. Thus, while our feedforward scheme slows the $X$-axis down, we achieve better bandwidth than we would with a simple low-pass filter.
